Tall

### 2022-08-31 graphs_newt_snakes/Heritability.Rmd
made a realy nice markdown-html (GA3). Also fixed up the last bit of confusion with the newt_snake snake_newt by making the facetwrap use sim which is what I use for everything else.

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

>>>>

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  #unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=factor(rep)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

### 2022-08-31 graphs_newt_snakes/Tall_GA1.Rmd
made a realy nice markdown-html (GA3). Also fixed up the last bit of confusion with the newt_snake snake_newt by making the facetwrap use sim which is what I use for everything else.

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=rep))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~snake_newt)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

>>>>

boxplot_cors_by_gen <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(rep), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
    geom_hline(yintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno),fill=rep))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  xlim(-1.1, 1.1)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

hist_cors_by_gen_col_rep_nofill <- function(file, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
  #file$newt_snake_rep <- paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$rep)
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  unique(file$sim)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=as.numeric(mean_newt_pheno_By_mean_snake_pheno)))+
  geom_vline(xintercept=real_snewt_cor, linetype="dashed")+
  geom_vline(xintercept=0, linetype="solid")+
  #geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  #geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  #geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  theme(plot.title = element_text(size=5)) +
  #stat_bin(bins=30)+
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())

@@

four_types_boxplot_cors_by_gen <- function(file,title, subt, x_label, y_label, min_gen, max_gen){
  file$snake_newt <- paste0( file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  plot <- ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ylim(-1.1, 1.1)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor("CA"), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), color = "CA"))+
  geom_boxplot(aes(x=factor("CB"), y=as.numeric(num_newts_By_num_snakes), color = "CB"))+
  geom_boxplot(aes(x=factor("CC"), y=as.numeric(sum_newt_pheno_By_num_snake), color = "CC"))+
  geom_boxplot(aes(x=factor("CD"), y=as.numeric(sum_snake_pheno_By_num_newt), color = "CD"))+
  geom_hline(yintercept=0, linetype="solid")+
  theme(plot.title = element_text(size=5)) +
  facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
